### 2023-05-05 main/frontmatter.tex
swap declaration-abstract order; add title and author

\begin{abstract}
Searching for new phenomena is an essential endeavour of experimental physics,
and is helped by guidance from plausible theoretical predictions.
This thesis presents such a search for signals of high-energy protons
scattering to massive resonances with dramatic decays, which are predicted by
supersymmetric models.%
% hack: hidden reference to constrain the reference numbering
\sbox0{\cite{atlas2022searches}}

>>>>

\begin{abstract}
\textbf{Title:} Two leptons, jets, and missing transverse momentum in ATLAS:
yet more non-evidence for supersymmetry

\noindent
\textbf{Author:} Rupert~Tombs
\\

Searching for new phenomena is an essential endeavour of experimental physics,
and is helped by guidance from plausible theoretical predictions.
This thesis presents such a search for signals of high-energy protons
scattering to massive resonances with dramatic decays, which are predicted by
supersymmetric models.%
% hack: hidden reference to constrain the reference numbering
\sbox0{\cite{atlas2022searches}}
